---
title: "Lake Elsinore image processing"
author: ""
output: 
  html_document:
    code_folding: hide
self_contained: yes
---

# {.tabset}

```{r, message = F, warning = F}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, fig.path = 'figs/', dev.args = list(bg = 'transparent'), eval = T)

library(raster)
library(sf)
library(tidyverse)
library(mapview)
library(proj4shortcut)
library(plotly)

prj_geo <- geo_wgs84
prj_pro <- utm_wgs84('11s')

```

## August 21st

Map of in situ samples with chlorophyll concentration. 

```{r}
# get coverage of in situ points by date
insit <- read_csv('raw/CHL_2017_08_21.csv', col_names = F) %>% 
  rename(
    site = X1, 
    lat = X2, 
    lon = X3, 
    chl = X4
  ) %>% 
  mutate(lat = ifelse(site == 34, 33.66954, lat)) 
coordinates(insit) <- ~ lon + lat
proj4string(insit) <- prj_geo
mapview(insit, zcol = 'chl', legend = T) 
```

Overlap of in situ samples (red numbers) with the spatial extent of each image. Note that the spatial extent is rectangular and not all pixels in the extent have values.
```{r fig.height = 7, fig.width = 5}
# transform insit to projected
insit <- spTransform(insit, CRS(prj_pro)) 

# raster tiffs
imgs_pth <- list.files('img/GeoTiff_08_21/', pattern = '^Raster*', full.names = T)

# get raster extents
out <- list()
cmbs <- for(i in 1:length(imgs_pth)){
  
  # raster aggregate, dissolve to polygon
  rst_chk <- stack(imgs_pth[[i]]) %>% 
    .[[1]] %>% 
    aggregate(fact = 10, fun = mean)
  values(rst_chk) <- ifelse(is.na(values(rst_chk)), NA, 1)
  ply <- rst_chk %>% 
    rasterToPolygons(dissolve = T)
  
  out[[i]] <- ply
  
}

# fortify polygons for plot
allply <- out %>% 
  map(., function(x){
    dat <- fortify(x) %>% 
      mutate(fl = gsub('\\.[0-9]$', '', names(x@data)))
    return(dat)
    }) %>% 
  enframe %>% 
  unnest

# plot
p <- ggplot() + 
  geom_polygon(data = allply, aes(x = long, y = lat, group = fl), alpha = 0.5) + 
  geom_text(data = data.frame(insit), aes(x = lon, y = lat, label = site)) + 
  coord_equal()
ggplotly(p)
```

Extracted pixel values for each of four bands in each image where sample sites occurred within an image.
```{r, cache = T}
# extract values from raster
out <- list()
for(i in 1:length(imgs_pth)){
  
  # cat(i, 'of', length(imgs_pth), '\n')
  
  # extract raster cells by points in insit
  rst <- stack(imgs_pth[[i]])
  crs(rst) <- prj_pro
  rst_chk  <- rst %>% 
    raster::extract(insit, buffer = 0) %>% 
    enframe %>% 
    bind_cols(insit@data, .) %>% 
    select(-name) %>% 
    filter(map(.$value, function(x) !anyNA(x)) %>% unlist) %>% 
    mutate(value = map(value, function(x){

      sumpt <- x %>% 
        data.frame(din = .) %>% 
        rownames_to_column('img_bnd') %>% 
        filter(!grepl('\\.5$', img_bnd))
      return(sumpt)
      
    })) %>% 
    unnest

  # append to output
  out[[i]] <- rst_chk

}

exts <- out %>% 
  do.call('rbind', .) %>% 
  remove_rownames() %>% 
  separate(img_bnd, c('img', 'bnd'), sep = '\\.') 
exts
```

Scatterplots of band values (din) with measured chlorophyll.
```{r fig.height = 4, fig.width  = 6}
toplo <- exts %>% 
  group_by(site, chl, bnd) %>% 
  summarise(din = mean(din))
ggplot(toplo, aes(x = din, y = chl)) + 
  geom_point() + 
  facet_wrap(~bnd, ncol = 2) + 
  stat_smooth(method = 'lm') + 
  theme_bw()
```

Working with model selection:
```{r}
library(caret)
library(MuMIn)
# https://pix4d.com/sequoia-faq/#3

tomod <- exts %>% 
  mutate(bnd = paste0('b', bnd)) %>% 
  spread(bnd, din)

glb <- lm(chl ~ (b1 + b2 + b2 + b3 + b4)^3 + I(b1^2) + I(b2^2) + I(b3^2) + I(b4^2), tomod, 
          na.action = 'na.pass')

tmp <- dredge(glb, evaluate = F)

# createFolds(1:nrow(tomod), k = 5)

```


## September 6th

Map of in situ samples with chlorophyll concentration. 

```{r}
# get coverage of in situ points by date
insit <- read_csv('raw/CHL_2017_09_06.csv', col_names = F) %>% 
  rename(
    site = X1, 
    lat = X2, 
    lon = X3, 
    chl = X4
  ) %>% 
  mutate(lon = ifelse(site == 39, -117.3597, lon))
coordinates(insit) <- ~ lon + lat
proj4string(insit) <- prj_geo
mapview(insit, zcol = 'chl', legend = T) 
```

Overlap of in situ samples (red numbers) with the spatial extent of each image. Note that the spatial extent is rectangular and not all pixels in the extent have values.
```{r fig.height = 7, fig.width = 7}
# transform insit to projected
insit <- spTransform(insit, CRS(prj_pro)) 

# raster tiffs
imgs_pth <- list.files('img/GeoTiff_09_06/', pattern = '*\\.tif$', full.names = T)

# get raster extents
out <- list()
cmbs <- for(i in 1:length(imgs_pth)){
  
  # raster aggregate, dissolve to polygon
  rst_chk <- stack(imgs_pth[[i]]) %>% 
    .[[1]] %>% 
    aggregate(fact = 10, fun = mean)
  values(rst_chk) <- ifelse(is.na(values(rst_chk)), NA, 1)
  ply <- rst_chk %>% 
    rasterToPolygons(dissolve = T)
  
  out[[i]] <- ply
  
}

# fortify polygons for plot
allply <- out %>% 
  map(., function(x){
    dat <- fortify(x) %>% 
      mutate(fl = gsub('\\.[0-9]$', '', names(x@data)))
    return(dat)
    }) %>% 
  enframe %>% 
  unnest

# plot
p <- ggplot() + 
  geom_polygon(data = allply, aes(x = long, y = lat, group = fl), alpha = 0.5) + 
  geom_text(data = data.frame(insit), aes(x = lon, y = lat, label = site)) + 
  coord_equal()
ggplotly(p)
```

Extracted pixel values for each of four bands in each image where sample sites occurred within an image.
```{r, cache = T}
# extract values from raster
out <- list()
for(i in 1:length(imgs_pth)){
  
  # cat(i, 'of', length(imgs_pth), '\n')
  
  rst <- stack(imgs_pth[[i]])
  crs(rst) <- prj_pro
  rst_chk  <- rst %>% 
    raster::extract(insit) %>% 
    data.frame(insit@data, .) %>%
    gather('img_bnd', 'din', -site, -chl) %>% 
    na.omit

  # out <- c(out, list(tmp))
  out[[i]] <- rst_chk

}

exts <- out %>% 
  do.call('rbind', .) %>% 
  remove_rownames() %>% 
  separate(img_bnd, c('img', 'bnd'), sep = '\\.')
exts
```

Scatterplots of band values (din) with measured chlorophyll.
```{r fig.height = 4, fig.width  = 6}
toplo <- exts %>% 
  group_by(site, chl, bnd) %>% 
  summarise(din = mean(din))
ggplot(toplo, aes(x = din, y = chl)) + 
  geom_point() + 
  facet_wrap(~bnd, ncol = 2) + 
  stat_smooth(method = 'lm') + 
  theme_bw()
```


